---
title: "Data Crunching Report: Data_quality- Draft not for distribution. "
author: "Generated with [Koboloader](https://unhcr.github.io/koboloadeR/docs) "
date: " `r format(Sys.Date(),  '%d %B %Y')`"
always_allow_html: yes
output:
  word_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    reference_docx: style-unhcr-portrait.docx
---
```{r setup, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir) - 5)
## Load all required packages
library(tidyverse)
library(ggthemes)
library(plyr)
library(ggrepel)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(corrplot)
library(reshape2)
library(scales)
library(survey)
library(knitr)
library(rmarkdown)
library(ggpubr)
library(grid)
library(koboloadeR)
options(scipen = 999) # turn-off scientific notation like 1e+48
## Provide below the name of the form in xsl form - format should be xls not xlsx
form <- "form.xls"
dico <- read.csv(paste0(mainDirroot,"/data/dico_",form,".csv"), encoding = "UTF-8", na.strings = "")
MainDataFrame <- read.csv(paste0(mainDirroot,"/data/MainDataFrame_encoded.csv"), encoding = "UTF-8", na.strings = "")
ListCaseNos <- read.csv(paste0(mainDirroot,"/data/ListCaseNos_encoded.csv"), encoding = "UTF-8", na.strings = "")
IndBiodata <- read.csv(paste0(mainDirroot,"/data/IndBiodata_encoded.csv"), encoding = "UTF-8", na.strings = "")


## label Variables
MainDataFrame <- kobo_label(MainDataFrame , dico)
ListCaseNos <- kobo_label(ListCaseNos , dico)
IndBiodata <- kobo_label(IndBiodata , dico)


## Set up ordinal Variables
list.ordinal <- as.character(unique(dico[ dico$listname == "diff_res" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Profile.ArrivalHist.DifRes <- factor(MainDataFrame$Profile.ArrivalHist.DifRes, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "grade" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam1 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam1, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam2 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam2, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam3 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam3, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam4 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam4, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.selfAssessment <- factor(MainDataFrame$Integration.PovertyPerception.selfAssessment, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.Isolation <- factor(MainDataFrame$Integration.Feeling.Isolation, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighoursConcern <- factor(MainDataFrame$Integration.Feeling.NeighoursConcern, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.ParticipateMeetings <- factor(MainDataFrame$Integration.Feeling.ParticipateMeetings, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighboursHelp <- factor(MainDataFrame$Integration.Feeling.NeighboursHelp, levels = list.ordinal)


## Create weighted survey object
MainDataFrame.survey <- svydesign(ids = ~ 1 ,  data = MainDataFrame )
ListCaseNos.survey <- svydesign(ids = ~ 1 ,  data = ListCaseNos )
IndBiodata.survey <- svydesign(ids = ~ 1 ,  data = IndBiodata )

```

# Introduction

This data crunching report allows to quickly explore the results of the survey that can be regenerated as needed.
You can:  
 
  *  adjust the configuration in the xlsform to break it into chapter;   

  *  configure disaggregation & correlation for each questions;   

  *  revise the data cleansing based on the cleaning log;   
 
  *  add weight to each observation in order to account for a specific sampling plan;  

  *  append calculated indicators to your data frame. 


The objective of this report is to allow to quickly identify potential patterns in your dataset.
                A quick screening of this initial report should allow to select the most meaningful graphs.
                A data digest from this initial report can be then reviewed through a __data analysis workshop__
                where subject matter experts can contribute with qualitative components.
                When analyzing those representations in a collective setting, you may:  
 
  *  __Reflect__: question data quality and/or make suggestions to change questions;   

  *  __Interpret__: develop qualitative interpretations of data patterns;   

  *  __Recommend__: develop recommendation in terms of programmatic adjustment;   

  *  __Classify__: order the level of sensitivity for the information;   

# Compilation of questions results

 
## Is the case reachable?
For audit purpose, it's important to have record of all attempt to reach cases selected in the sample


Single choice question 


### Tabulation
```{r CaseReachable.reachable.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$CaseReachable.reachable))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "reachable"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$CaseReachable.reachable, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$CaseReachable.reachable,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ CaseReachable.reachable, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Is the case reachable?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r CaseReachable.reachable1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~CaseReachable.reachable + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Is the case reachable? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)


```{r CaseReachable.reachableccc1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$CaseReachable.reachable,MainDataFrame$dependency.cat)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$CaseReachable.reachable,MainDataFrame$dependency.cat)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
Is the case reachable? (row)
 & Dependency ratio - Discrete (col)")) 

```


 
## Select the reason case is unreachable:
For audit purpose, it's important to have record of reasons why cases selected in the sample could not be reached


Single choice question 


### Tabulation
```{r CaseReachable.NotReachable.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8.33333333333333, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$CaseReachable.NotReachable))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "NotReachable"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$CaseReachable.NotReachable, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$CaseReachable.NotReachable,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ CaseReachable.NotReachable, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Select the reason case is unreachable:",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r CaseReachable.NotReachable1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~CaseReachable.NotReachable + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Select the reason case is unreachable: (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Organization of enumerator:
NA


Single choice question 


### Tabulation
```{r EnumeratorDetails.Organization.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=5, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$EnumeratorDetails.Organization))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "Organization"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$EnumeratorDetails.Organization, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$EnumeratorDetails.Organization,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ EnumeratorDetails.Organization, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Organization of enumerator:",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r EnumeratorDetails.Organization1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~EnumeratorDetails.Organization + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Organization of enumerator: (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## District
Optional as a fallback


Single choice question 


### Tabulation
```{r Location.LocationDistrict.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Location.LocationDistrict))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "LocationDistrict"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Location.LocationDistrict, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Location.LocationDistrict,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Location.LocationDistrict, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("District",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations




### Significant Associations (chi-square with p value < 5%)


```{r Location.LocationDistrictccc1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Location.LocationDistrict,MainDataFrame$hh.child.head)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Location.LocationDistrict,MainDataFrame$hh.child.head)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
District (row)
 & Cases headed by child (under 18) (col)")) 

```


```{r Location.LocationDistrictccc2.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Location.LocationDistrict,MainDataFrame$hh.elder.head)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Location.LocationDistrict,MainDataFrame$hh.elder.head)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
District (row)
 & Cases headed by elder (above 59) (col)")) 

```


 
## Area
Optional as a fallback


Single choice question 


### Tabulation
```{r Location.LocationLevel2.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=21.6666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Location.LocationLevel2))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "LocationLevel2"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Location.LocationLevel2, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Location.LocationLevel2,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Location.LocationLevel2, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Area",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Location.LocationLevel21.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Location.LocationLevel2 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Area (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...

##### Page Break
