---
title: "Data Crunching Report: Documentation- Draft not for distribution. "
author: "Generated with [Koboloader](https://unhcr.github.io/koboloadeR/docs) "
date: " `r format(Sys.Date(),  '%d %B %Y')`"
always_allow_html: yes
output:
  word_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    reference_docx: style-unhcr-portrait.docx
---
```{r setup, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir) - 5)
## Load all required packages
library(tidyverse)
library(ggthemes)
library(plyr)
library(ggrepel)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(corrplot)
library(reshape2)
library(scales)
library(survey)
library(knitr)
library(rmarkdown)
library(ggpubr)
library(grid)
library(koboloadeR)
options(scipen = 999) # turn-off scientific notation like 1e+48
## Provide below the name of the form in xsl form - format should be xls not xlsx
form <- "form.xls"
dico <- read.csv(paste0(mainDirroot,"/data/dico_",form,".csv"), encoding = "UTF-8", na.strings = "")
MainDataFrame <- read.csv(paste0(mainDirroot,"/data/MainDataFrame_encoded.csv"), encoding = "UTF-8", na.strings = "")
ListCaseNos <- read.csv(paste0(mainDirroot,"/data/ListCaseNos_encoded.csv"), encoding = "UTF-8", na.strings = "")
IndBiodata <- read.csv(paste0(mainDirroot,"/data/IndBiodata_encoded.csv"), encoding = "UTF-8", na.strings = "")


## label Variables
MainDataFrame <- kobo_label(MainDataFrame , dico)
ListCaseNos <- kobo_label(ListCaseNos , dico)
IndBiodata <- kobo_label(IndBiodata , dico)


## Set up ordinal Variables
list.ordinal <- as.character(unique(dico[ dico$listname == "diff_res" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Profile.ArrivalHist.DifRes <- factor(MainDataFrame$Profile.ArrivalHist.DifRes, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "grade" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam1 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam1, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam2 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam2, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam3 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam3, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam4 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam4, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.selfAssessment <- factor(MainDataFrame$Integration.PovertyPerception.selfAssessment, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.Isolation <- factor(MainDataFrame$Integration.Feeling.Isolation, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighoursConcern <- factor(MainDataFrame$Integration.Feeling.NeighoursConcern, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.ParticipateMeetings <- factor(MainDataFrame$Integration.Feeling.ParticipateMeetings, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighboursHelp <- factor(MainDataFrame$Integration.Feeling.NeighboursHelp, levels = list.ordinal)


## Create weighted survey object
MainDataFrame.survey <- svydesign(ids = ~ 1 ,  data = MainDataFrame )
ListCaseNos.survey <- svydesign(ids = ~ 1 ,  data = ListCaseNos )
IndBiodata.survey <- svydesign(ids = ~ 1 ,  data = IndBiodata )

```

# Introduction

This data crunching report allows to quickly explore the results of the survey that can be regenerated as needed.
You can:  
 
  *  adjust the configuration in the xlsform to break it into chapter;   

  *  configure disaggregation & correlation for each questions;   

  *  revise the data cleansing based on the cleaning log;   
 
  *  add weight to each observation in order to account for a specific sampling plan;  

  *  append calculated indicators to your data frame. 


The objective of this report is to allow to quickly identify potential patterns in your dataset.
                A quick screening of this initial report should allow to select the most meaningful graphs.
                A data digest from this initial report can be then reviewed through a __data analysis workshop__
                where subject matter experts can contribute with qualitative components.
                When analyzing those representations in a collective setting, you may:  
 
  *  __Reflect__: question data quality and/or make suggestions to change questions;   

  *  __Interpret__: develop qualitative interpretations of data patterns;   

  *  __Recommend__: develop recommendation in terms of programmatic adjustment;   

  *  __Classify__: order the level of sensitivity for the information;   

# Compilation of questions results

 
## Has anyone in the household experienced difficulties and/or been unable to regis
NA


Single choice question 


### Tabulation
```{r Profile.ArrivalHist.RegDiff.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Profile.ArrivalHist.RegDiff))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "RegDiff"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Profile.ArrivalHist.RegDiff, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Profile.ArrivalHist.RegDiff,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.ArrivalHist.RegDiff, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Has anyone in the household experienced difficulties and/or been unable to regis",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.ArrivalHist.RegDiff1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.ArrivalHist.RegDiff + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Has anyone in the household experienced difficulties and/or been unable to regis (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)


```{r Profile.ArrivalHist.RegDiffccc1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Profile.ArrivalHist.RegDiff,MainDataFrame$agechef.cat2)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Profile.ArrivalHist.RegDiff,MainDataFrame$agechef.cat2)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
Has anyone in the household experienced difficulties and/or been unable to regis (row)
 & Age of main respondent / head of household - Categories 2 (col)")) 

```


 
## What difficulties were experienced?
NA


Multiple choice question  


### Tabulation

```{r Profile.ArrivalHist.DiffEncoun.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="difficulties" & grepl("DiffEncoun",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "DiffEncoun"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("What difficulties were experienced?",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Profile.ArrivalHist.DiffEncoun.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## Have these difficulties been resolved?
NA


Single choice question 


### Tabulation
```{r Profile.ArrivalHist.DifRes.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=3.33333333333333, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Profile.ArrivalHist.DifRes))
list.ordinal <- as.character(unique(dico[ dico$listname == "diff_res" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "DifRes"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Profile.ArrivalHist.DifRes, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Profile.ArrivalHist.DifRes,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.ArrivalHist.DifRes, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "diff_res" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Have these difficulties been resolved?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.ArrivalHist.DifRes1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.ArrivalHist.DifRes + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Have these difficulties been resolved? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)


```{r Profile.ArrivalHist.DifResccc1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Profile.ArrivalHist.DifRes,MainDataFrame$hh.elder.head)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Profile.ArrivalHist.DifRes,MainDataFrame$hh.elder.head)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
Have these difficulties been resolved? (row)
 & Cases headed by elder (above 59) (col)")) 

```


 
## Are there any household members without regularized legal residency in this coun
NA


Single choice question 


### Tabulation
```{r Protection.Documentation.LegalResidency.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Protection.Documentation.LegalResidency))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "LegalResidency"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Protection.Documentation.LegalResidency, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Protection.Documentation.LegalResidency,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Protection.Documentation.LegalResidency, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Are there any household members without regularized legal residency in this coun",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Protection.Documentation.LegalResidency1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Protection.Documentation.LegalResidency + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Are there any household members without regularized legal residency in this coun (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)


```{r Protection.Documentation.LegalResidencyccc1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Protection.Documentation.LegalResidency,MainDataFrame$hh.child.head)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Protection.Documentation.LegalResidency,MainDataFrame$hh.child.head)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
Are there any household members without regularized legal residency in this coun (row)
 & Cases headed by child (under 18) (col)")) 

```


```{r Protection.Documentation.LegalResidencyccc2.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Protection.Documentation.LegalResidency,MainDataFrame$has.baby)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Protection.Documentation.LegalResidency,MainDataFrame$has.baby)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
Are there any household members without regularized legal residency in this coun (row)
 & Household has kids of less than 2 years old (col)")) 

```


 
## Reasons for illegal residence:
NA


Multiple choice question  


### Tabulation

```{r Protection.Documentation.IllegalResidency.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="ir_reasons" & grepl("IllegalResidency",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "IllegalResidency"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Reasons for illegal residence:",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Protection.Documentation.IllegalResidency.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## Were any children in the household born after leaving CoO?
NA


Single choice question 


### Tabulation
```{r Protection.Documentation.ChildBirth.ChildBirthAbroad.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=2.5, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthAbroad))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "ChildBirthAbroad"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthAbroad, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthAbroad,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Protection.Documentation.ChildBirth.ChildBirthAbroad, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Were any children in the household born after leaving CoO?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Protection.Documentation.ChildBirth.ChildBirthAbroad1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Protection.Documentation.ChildBirth.ChildBirthAbroad + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Were any children in the household born after leaving CoO? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## If so, how many?
NA


Numeric question  


### Tabulation

```{r Protection.Documentation.ChildBirth.ChildBirthHowMany.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthHowMany <- as.numeric(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthHowMany)
frequ <- as.data.frame(table(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthHowMany))
cat("No responses recorded for this question...")
cat("No responses recorded for this question...")

```



 
## How many of them have birth certificates?
NA


Numeric question  


### Tabulation

```{r Protection.Documentation.ChildBirth.ChildBirthCertificates.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthCertificates <- as.numeric(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthCertificates)
frequ <- as.data.frame(table(MainDataFrame$Protection.Documentation.ChildBirth.ChildBirthCertificates))
cat("No responses recorded for this question...")
cat("No responses recorded for this question...")

```



 
## What document do you have to prove the birth of your child? (select only the hig
NA


Single choice question 


cat("No responses or only one modality recorded for this question...")

```









 
## Do any members of the household own property in CoA?
NA


Single choice question 


### Tabulation
```{r Protection.HLP.Housing.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Protection.HLP.Housing))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "Housing"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.Housing, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.Housing,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Protection.HLP.Housing, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Do any members of the household own property in CoA?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Protection.HLP.Housing1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Protection.HLP.Housing + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Do any members of the household own property in CoA? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## What is the status of the land on which you resided in Syria?
NA


Single choice question 


### Tabulation
```{r Protection.HLP.LandStatusResided.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=5.83333333333333, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Protection.HLP.LandStatusResided))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "LandStatusResided"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.LandStatusResided, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.LandStatusResided,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Protection.HLP.LandStatusResided, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("What is the status of the land on which you resided in Syria?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Protection.HLP.LandStatusResided1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Protection.HLP.LandStatusResided + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("What is the status of the land on which you resided in Syria? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## What type of documentation did you have proving ownership or right of usage of t
NA


Single choice question 


### Tabulation
```{r Protection.HLP.OwnershipOrRightOf.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=5, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Protection.HLP.OwnershipOrRightOf))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "OwnershipOrRightOf"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.OwnershipOrRightOf, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.OwnershipOrRightOf,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Protection.HLP.OwnershipOrRightOf, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("What type of documentation did you have proving ownership or right of usage of t",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Protection.HLP.OwnershipOrRightOf1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Protection.HLP.OwnershipOrRightOf + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("What type of documentation did you have proving ownership or right of usage of t (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## What is the current status of this land?
NA


Single choice question 


### Tabulation
```{r Protection.HLP.CurrentStatusForLand.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=5.83333333333333, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Protection.HLP.CurrentStatusForLand))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "CurrentStatusForLand"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.CurrentStatusForLand, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Protection.HLP.CurrentStatusForLand,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Protection.HLP.CurrentStatusForLand, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("What is the current status of this land?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Protection.HLP.CurrentStatusForLand1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Protection.HLP.CurrentStatusForLand + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("What is the current status of this land? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)


```{r Protection.HLP.CurrentStatusForLandccc1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6, size="small"}
corrplot(chisq.test(MainDataFrame$Protection.HLP.CurrentStatusForLand,MainDataFrame$female.ratio.cat)$residuals,
is.cor = FALSE, # use for general matrix to convert to Sq form
cl.pos = "n", ## Do not display the color legend
cl.cex = 0.7, # Size of all label
tl.cex = 0.7, # Size of axis label
tl.srt = 45, # string rotation in degrees
tl.col = "black", # color of text label.
addCoef.col = "grey", # add coeff in the chart
number.cex= 3/ncol(chisq.test(MainDataFrame$Protection.HLP.CurrentStatusForLand,MainDataFrame$female.ratio.cat)), # size of coeff
mar = c(0.5,0.5,4, 0.5), ## margin of plots
title= paste0("Correlation between
What is the current status of this land? (row)
 & Female Ratio - Discrete (col)")) 

```

##### Page Break
