---
title: "Data Crunching Report: Health- Draft not for distribution. "
author: "Generated with [Koboloader](https://unhcr.github.io/koboloadeR/docs) "
date: " `r format(Sys.Date(),  '%d %B %Y')`"
always_allow_html: yes
output:
  word_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    reference_docx: style-unhcr-portrait.docx
---
```{r setup, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir) - 5)
## Load all required packages
library(tidyverse)
library(ggthemes)
library(plyr)
library(ggrepel)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(corrplot)
library(reshape2)
library(scales)
library(survey)
library(knitr)
library(rmarkdown)
library(ggpubr)
library(grid)
library(koboloadeR)
options(scipen = 999) # turn-off scientific notation like 1e+48
## Provide below the name of the form in xsl form - format should be xls not xlsx
form <- "form.xls"
dico <- read.csv(paste0(mainDirroot,"/data/dico_",form,".csv"), encoding = "UTF-8", na.strings = "")
MainDataFrame <- read.csv(paste0(mainDirroot,"/data/MainDataFrame_encoded.csv"), encoding = "UTF-8", na.strings = "")
ListCaseNos <- read.csv(paste0(mainDirroot,"/data/ListCaseNos_encoded.csv"), encoding = "UTF-8", na.strings = "")
IndBiodata <- read.csv(paste0(mainDirroot,"/data/IndBiodata_encoded.csv"), encoding = "UTF-8", na.strings = "")


## label Variables
MainDataFrame <- kobo_label(MainDataFrame , dico)
ListCaseNos <- kobo_label(ListCaseNos , dico)
IndBiodata <- kobo_label(IndBiodata , dico)


## Set up ordinal Variables
list.ordinal <- as.character(unique(dico[ dico$listname == "diff_res" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Profile.ArrivalHist.DifRes <- factor(MainDataFrame$Profile.ArrivalHist.DifRes, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "grade" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam1 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam1, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam2 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam2, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam3 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam3, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam4 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam4, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.selfAssessment <- factor(MainDataFrame$Integration.PovertyPerception.selfAssessment, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.Isolation <- factor(MainDataFrame$Integration.Feeling.Isolation, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighoursConcern <- factor(MainDataFrame$Integration.Feeling.NeighoursConcern, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.ParticipateMeetings <- factor(MainDataFrame$Integration.Feeling.ParticipateMeetings, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighboursHelp <- factor(MainDataFrame$Integration.Feeling.NeighboursHelp, levels = list.ordinal)


## Create weighted survey object
MainDataFrame.survey <- svydesign(ids = ~ 1 ,  data = MainDataFrame )
ListCaseNos.survey <- svydesign(ids = ~ 1 ,  data = ListCaseNos )
IndBiodata.survey <- svydesign(ids = ~ 1 ,  data = IndBiodata )

```

# Introduction

This data crunching report allows to quickly explore the results of the survey that can be regenerated as needed.
You can:  
 
  *  adjust the configuration in the xlsform to break it into chapter;   

  *  configure disaggregation & correlation for each questions;   

  *  revise the data cleansing based on the cleaning log;   
 
  *  add weight to each observation in order to account for a specific sampling plan;  

  *  append calculated indicators to your data frame. 


The objective of this report is to allow to quickly identify potential patterns in your dataset.
                A quick screening of this initial report should allow to select the most meaningful graphs.
                A data digest from this initial report can be then reviewed through a __data analysis workshop__
                where subject matter experts can contribute with qualitative components.
                When analyzing those representations in a collective setting, you may:  
 
  *  __Reflect__: question data quality and/or make suggestions to change questions;   

  *  __Interpret__: develop qualitative interpretations of data patterns;   

  *  __Recommend__: develop recommendation in terms of programmatic adjustment;   

  *  __Classify__: order the level of sensitivity for the information;   

# Compilation of questions results

 
## Does Individual have any of the following specific needs
Change to serious medical condition or chronic disease


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "SpecificNeeds"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Does Individual have any of the following specific needs",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.SpecNeeds.SpecificNeeds + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Does Individual have any of the following specific needs (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Do you have difficulty seeing, even if wearing glasses?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty))
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "SeeingDifficulty"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty seeing, even if wearing glasses?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty seeing, even if wearing glasses? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Do you have difficulty hearing, even if wearing a hearing aid?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty))
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "HearingDifficulty"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty hearing, even if wearing a hearing aid?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty hearing, even if wearing a hearing aid? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Do you have difficulty walking or climbing steps?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty))
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "WalkingDifficulty"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty walking or climbing steps?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty walking or climbing steps? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Do you  have difficulty remembering or concentrating?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty))
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "RememberingDifficulty"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Do you  have difficulty remembering or concentrating?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Do you  have difficulty remembering or concentrating? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Do you have difficulty (with self-care such as) washing all over or dressing?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty))
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "SelfCareDifficulty"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty (with self-care such as) washing all over or dressing?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Do you have difficulty (with self-care such as) washing all over or dressing? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Using your normal customary language, do you have difficulty communicating, for
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty))
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ$Var1) <- list.ordinal
names(frequ)[1] <- "CommunicatingDifficulty"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
levels(frequ3$Var1) <- list.ordinal
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Using your normal customary language, do you have difficulty communicating, for",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Using your normal customary language, do you have difficulty communicating, for (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Does Individual need assistance from another person to use the toilet?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=2.5, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "NeedAssistance"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Does Individual need assistance from another person to use the toilet?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.NeedAssistance + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Does Individual need assistance from another person to use the toilet? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Is there a caregiver available?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "AvailableCaregiver"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Is there a caregiver available?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.AvailableCaregiver + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Is there a caregiver available? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Does Individual have access to a toilet/bathroom adapted to their disability?
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=3.33333333333333, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "AccessDisToilet"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Does Individual have access to a toilet/bathroom adapted to their disability?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Impairment.AccessDisToilet + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Does Individual have access to a toilet/bathroom adapted to their disability? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## About how often during the last two weeks did you feel so afraid that nothing co
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "AfraidThatNothing"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("About how often during the last two weeks did you feel so afraid that nothing co",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Emotions.AfraidThatNothing + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("About how often during the last two weeks did you feel so afraid that nothing co (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## About how often during the last two weeks did you feel so angry that you felt ou
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "FeltOutOfControl"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("About how often during the last two weeks did you feel so angry that you felt ou",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Emotions.FeltOutOfControl + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("About how often during the last two weeks did you feel so angry that you felt ou (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## During the last two weeks, about how often did you feel so uninterested in thing
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "UninterestedInThings"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("During the last two weeks, about how often did you feel so uninterested in thing",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Emotions.UninterestedInThings + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("During the last two weeks, about how often did you feel so uninterested in thing (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## During the last two weeks, about how often did you feel so hopeless that you did
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "Hopeless"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("During the last two weeks, about how often did you feel so hopeless that you did",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Emotions.Hopeless + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("During the last two weeks, about how often did you feel so hopeless that you did (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## You may have experienced one or more events that have been intensely upsetting t
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "IntenselyUpsetting"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("You may have experienced one or more events that have been intensely upsetting t",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Emotions.IntenselyUpsetting + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("You may have experienced one or more events that have been intensely upsetting t (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## The next question is about how these feelings of fear, anger, fatigue, disintere
NA


Single choice question 


### Tabulation
```{r Profile.CaseNoDetails.IndBiodata.Emotions.Anger.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=6.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.Anger))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "Anger"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.Anger, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(IndBiodata$Profile.CaseNoDetails.IndBiodata.Emotions.Anger,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Profile.CaseNoDetails.IndBiodata.Emotions.Anger, design = IndBiodata.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("The next question is about how these feelings of fear, anger, fatigue, disintere",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Profile.CaseNoDetails.IndBiodata.Emotions.Anger1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Profile.CaseNoDetails.IndBiodata.Emotions.Anger + Location.LocationDistrict, design =IndBiodata.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("The next question is about how these feelings of fear, anger, fatigue, disintere (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

No correlation requested for this question...



 
## Did any household members require primary health care in the past 6 months?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.HealthRequired1.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.HealthRequired1))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "HealthRequired1"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthRequired1, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthRequired1,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.HealthRequired1, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Did any household members require primary health care in the past 6 months?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.HealthRequired11.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.HealthRequired1 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Did any household members require primary health care in the past 6 months? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Did the household member(s) receive the required primary health care assistance?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.HealthAccess1.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.HealthAccess1))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "HealthAccess1"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthAccess1, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthAccess1,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.HealthAccess1, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Did the household member(s) receive the required primary health care assistance?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.HealthAccess11.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.HealthAccess1 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Did the household member(s) receive the required primary health care assistance? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Why were household members unable to receive the required primary health assista
NA


Multiple choice question  


### Tabulation

```{r Assistance.Health.HealthAccessBar.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="barriers_health" & grepl("HealthAccessBar",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "HealthAccessBar"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Why were household members unable to receive the required primary health assista",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Assistance.Health.HealthAccessBar.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## Where did the household member(s) access primary healthcare?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.HealthcareAccess.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.HealthcareAccess))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "HealthcareAccess"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthcareAccess, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthcareAccess,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.HealthcareAccess, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Where did the household member(s) access primary healthcare?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.HealthcareAccess1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.HealthcareAccess + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Where did the household member(s) access primary healthcare? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Why did the household member(s) seek a private clinic?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.PrivClinicYes.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=5, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.PrivClinicYes))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "PrivClinicYes"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.PrivClinicYes, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.PrivClinicYes,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.PrivClinicYes, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Why did the household member(s) seek a private clinic?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.PrivClinicYes1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.PrivClinicYes + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Why did the household member(s) seek a private clinic? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Did any of your household members require hospitalization in the past 6 months?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.HealthRequired2.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.HealthRequired2))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "HealthRequired2"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthRequired2, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthRequired2,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.HealthRequired2, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Did any of your household members require hospitalization in the past 6 months?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.HealthRequired21.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.HealthRequired2 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Did any of your household members require hospitalization in the past 6 months? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Did the household member(s) receive the required hospital care?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.HealthAccess2.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.HealthAccess2))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "HealthAccess2"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthAccess2, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthAccess2,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.HealthAccess2, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Did the household member(s) receive the required hospital care?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.HealthAccess21.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.HealthAccess2 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Did the household member(s) receive the required hospital care? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Why were household member(s) unable to receive the required hospital care?
NA


Multiple choice question  


### Tabulation

```{r Assistance.Health.HealthAccessBar2.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="barriers_health1" & grepl("HealthAccessBar2",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "HealthAccessBar2"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Why were household member(s) unable to receive the required hospital care?",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Assistance.Health.HealthAccessBar2.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## Where did the household member(s) access hospitalization?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.HealthcareAccess2.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=3.33333333333333, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.HealthcareAccess2))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "HealthcareAccess2"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthcareAccess2, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.HealthcareAccess2,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.HealthcareAccess2, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Where did the household member(s) access hospitalization?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.HealthcareAccess21.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.HealthcareAccess2 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Where did the household member(s) access hospitalization? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Why did the household member(s) seek a private clinic?
NA


Single choice question 


### Tabulation
```{r Assistance.Health.PrivClinicYes2.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4.16666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.PrivClinicYes2))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "PrivClinicYes2"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.PrivClinicYes2, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.PrivClinicYes2,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.PrivClinicYes2, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Why did the household member(s) seek a private clinic?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.PrivClinicYes21.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.PrivClinicYes2 + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Why did the household member(s) seek a private clinic? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## If anyone in the household requires urgent medical attention, do you know how to
NA


Single choice question 


### Tabulation
```{r Assistance.Health.LifeSavingMedical.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.Health.LifeSavingMedical))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "LifeSavingMedical"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.LifeSavingMedical, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.Health.LifeSavingMedical,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.Health.LifeSavingMedical, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("If anyone in the household requires urgent medical attention, do you know how to",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.Health.LifeSavingMedical1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.Health.LifeSavingMedical + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("If anyone in the household requires urgent medical attention, do you know how to (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...

##### Page Break
