---
title: "Data Crunching Report: Budget_analysis- Draft not for distribution. "
author: "Generated with [Koboloader](https://unhcr.github.io/koboloadeR/docs) "
date: " `r format(Sys.Date(),  '%d %B %Y')`"
always_allow_html: yes
output:
  word_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    reference_docx: style-unhcr-portrait.docx
---
```{r setup, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
mainDir <- getwd()
mainDirroot <- substring(mainDir, 0 , nchar(mainDir) - 5)
## Load all required packages
library(tidyverse)
library(ggthemes)
library(plyr)
library(ggrepel)
library(viridis)
library(RColorBrewer)
library(extrafont)
library(corrplot)
library(reshape2)
library(scales)
library(survey)
library(knitr)
library(rmarkdown)
library(ggpubr)
library(grid)
library(koboloadeR)
options(scipen = 999) # turn-off scientific notation like 1e+48
## Provide below the name of the form in xsl form - format should be xls not xlsx
form <- "form.xls"
dico <- read.csv(paste0(mainDirroot,"/data/dico_",form,".csv"), encoding = "UTF-8", na.strings = "")
MainDataFrame <- read.csv(paste0(mainDirroot,"/data/MainDataFrame_encoded.csv"), encoding = "UTF-8", na.strings = "")
ListCaseNos <- read.csv(paste0(mainDirroot,"/data/ListCaseNos_encoded.csv"), encoding = "UTF-8", na.strings = "")
IndBiodata <- read.csv(paste0(mainDirroot,"/data/IndBiodata_encoded.csv"), encoding = "UTF-8", na.strings = "")


## label Variables
MainDataFrame <- kobo_label(MainDataFrame , dico)
ListCaseNos <- kobo_label(ListCaseNos , dico)
IndBiodata <- kobo_label(IndBiodata , dico)


## Set up ordinal Variables
list.ordinal <- as.character(unique(dico[ dico$listname == "diff_res" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Profile.ArrivalHist.DifRes <- factor(MainDataFrame$Profile.ArrivalHist.DifRes, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "grade" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.YouthEduc.SchoolLevel.GradeLevel, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SeeingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.HearingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.WalkingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.RememberingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.SelfCareDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "MedicalDifficulty" & dico$type == "select_one_d", c("labelchoice") ]))
IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty <- factor(IndBiodata$Profile.CaseNoDetails.IndBiodata.Impairment.CommunicatingDifficulty, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam1 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam1, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam2 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam2, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam3 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam3, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.vignetteFam4 <- factor(MainDataFrame$Integration.PovertyPerception.vignetteFam4, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "poverty_ladder" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.PovertyPerception.selfAssessment <- factor(MainDataFrame$Integration.PovertyPerception.selfAssessment, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.Isolation <- factor(MainDataFrame$Integration.Feeling.Isolation, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighoursConcern <- factor(MainDataFrame$Integration.Feeling.NeighoursConcern, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.ParticipateMeetings <- factor(MainDataFrame$Integration.Feeling.ParticipateMeetings, levels = list.ordinal)
list.ordinal <- as.character(unique(dico[ dico$listname == "opinion" & dico$type == "select_one_d", c("labelchoice") ]))
MainDataFrame$Integration.Feeling.NeighboursHelp <- factor(MainDataFrame$Integration.Feeling.NeighboursHelp, levels = list.ordinal)


## Create weighted survey object
MainDataFrame.survey <- svydesign(ids = ~ 1 ,  data = MainDataFrame )
ListCaseNos.survey <- svydesign(ids = ~ 1 ,  data = ListCaseNos )
IndBiodata.survey <- svydesign(ids = ~ 1 ,  data = IndBiodata )

```

# Introduction

This data crunching report allows to quickly explore the results of the survey that can be regenerated as needed.
You can:  
 
  *  adjust the configuration in the xlsform to break it into chapter;   

  *  configure disaggregation & correlation for each questions;   

  *  revise the data cleansing based on the cleaning log;   
 
  *  add weight to each observation in order to account for a specific sampling plan;  

  *  append calculated indicators to your data frame. 


The objective of this report is to allow to quickly identify potential patterns in your dataset.
                A quick screening of this initial report should allow to select the most meaningful graphs.
                A data digest from this initial report can be then reviewed through a __data analysis workshop__
                where subject matter experts can contribute with qualitative components.
                When analyzing those representations in a collective setting, you may:  
 
  *  __Reflect__: question data quality and/or make suggestions to change questions;   

  *  __Interpret__: develop qualitative interpretations of data patterns;   

  *  __Recommend__: develop recommendation in terms of programmatic adjustment;   

  *  __Classify__: order the level of sensitivity for the information;   

# Compilation of questions results

 
## Does your household currently have access to the following items to cover househ
NA


Multiple choice question  


### Tabulation

```{r Welfare.AssetsBudgets.Assets.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="assets" & grepl("Assets",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "Assets"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Does your household currently have access to the following items to cover househ",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.AssetsBudgets.Assets.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## During the past 3 months (90 days), did any member of the household borrow money
NA


Single choice question 


### Tabulation
```{r Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "BorrowedYesNo"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("During the past 3 months (90 days), did any member of the household borrow money",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Welfare.IncomeExpenditure.BorrowingDebt.BorrowedYesNo + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("During the past 3 months (90 days), did any member of the household borrow money (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## Please specify - member of the household borrowed money and/or received credit
NA


Multiple choice question  


### Tabulation

```{r Welfare.IncomeExpenditure.BorrowingDebt.Borrowed.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="borrowing" & grepl("Borrowed",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "Borrowed"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Please specify - member of the household borrowed money and/or received credit",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.BorrowingDebt.Borrowed.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## What were the primary reasons for borrowing?
NA


Multiple choice question  


### Tabulation

```{r Welfare.IncomeExpenditure.BorrowingDebt.ReasonBorrowing.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="borrow_reason" & grepl("ReasonBorrowing",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "ReasonBorrowing"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("What were the primary reasons for borrowing?",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.BorrowingDebt.ReasonBorrowing.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## From whom did you get the credit or borrow the money?
NA


Multiple choice question  


### Tabulation

```{r Welfare.IncomeExpenditure.BorrowingDebt.SourceBorrowing.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="borrowing_sources" & grepl("SourceBorrowing",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "SourceBorrowing"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("From whom did you get the credit or borrow the money?",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.BorrowingDebt.SourceBorrowing.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## What is the current total debt up to now from borrowing money that has not yet b
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("What is the current total debt up to now from borrowing money that has not yet b",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("What is the current total debt up to now from borrowing money that has not yet b",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.BorrowingDebt.TotalDebtx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalDebt , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("What is the current total debt up to now from borrowing money that has not yet b",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("What is the current total debt up to now from borrowing money that has not yet b",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## What is the current total debt up to now from receiving credit that has not yet
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("What is the current total debt up to now from receiving credit that has not yet",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("What is the current total debt up to now from receiving credit that has not yet",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.BorrowingDebt.TotalCreditx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.BorrowingDebt.TotalCredit , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("What is the current total debt up to now from receiving credit that has not yet",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("What is the current total debt up to now from receiving credit that has not yet",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## In the past 30 days, what was the MAIN source of cash/income used to sustain you
NA


Single choice question 


### Tabulation
```{r Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=16.6666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "TopIncomeSources"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("In the past 30 days, what was the MAIN source of cash/income used to sustain you",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Welfare.IncomeExpenditure.Income.IncomeSources.TopIncomeSources + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("In the past 30 days, what was the MAIN source of cash/income used to sustain you (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...


 
## In the past 30 days, what would you say were other main sources of cash/income u
NA


Multiple choice question  


### Tabulation

```{r Welfare.IncomeExpenditure.Income.IncomeSources.OtherIncomeSource.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=8, size="small"}

### Tabulation
##Compute contengency table
selectmultilist1 <- as.data.frame(dico[dico$type == "select_multiple" & dico$listname=="income_source" & grepl("OtherIncomeSource",dico$fullname)==TRUE , c("fullname")])
names(selectmultilist1)[1] <- "check"
check <- as.data.frame(names(MainDataFrame))
names(check)[1] <- "check"
check$id <- row.names(check)
check <- merge(x = check, y = selectmultilist1, by = "check")
selectmultilist <- as.character(check[ ,1])
## Reshape answers
data.selectmultilist <- MainDataFrame[ selectmultilist ]
data.selectmultilist$id <- rownames(data.selectmultilist)
totalanswer <- nrow(data.selectmultilist)
data.selectmultilist <- data.selectmultilist[ data.selectmultilist[ ,1]!="Not replied", ]
percentreponse <- paste0(round((nrow(data.selectmultilist)/totalanswer)*100,digits = 1),"%")
meltdata <- melt(data.selectmultilist,id="id")
castdata <- as.data.frame(table(meltdata[c("value")]))
castdata$freqper <- castdata$Freq/nrow(data.selectmultilist)
castdata <- castdata[castdata$Var1!="Not selected", ]
castdata$Var1 <- factor(castdata$Var1, levels=castdata[order(castdata$freqper), "Var1"])
frequ <- castdata[castdata$Var1!="", ]
## display table
names(frequ)[1] <- "OtherIncomeSource"
frequ[ ,3] <- paste0(round(frequ[ ,3]*100,digits = 1),"%")
frequ1 <- castdata[castdata$Var1!="", ]
frequ1[ ,4] <- paste0(round(frequ1[ ,3]*100,digits = 1),"%")
names(frequ1)[4] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ1, aes(x=Var1, y=freqper)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = freqper, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("In the past 30 days, what would you say were other main sources of cash/income u",
subtitle = paste0("Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Income.IncomeSources.OtherIncomeSource.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


```


 
## What is the total amount of remittances from friends and family outside the coun
Add comment that constraint has to be changed according to local currency norms


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("What is the total amount of remittances from friends and family outside the coun",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("What is the total amount of remittances from friends and family outside the coun",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotalx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.RemittancesTotal , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("What is the total amount of remittances from friends and family outside the coun",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("What is the total amount of remittances from friends and family outside the coun",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## In the past 30 days, what was the total income (from employment) of all the hous
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("In the past 30 days, what was the total income (from employment) of all the hous",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("In the past 30 days, what was the total income (from employment) of all the hous",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotalx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Income.IncomeSources.IncomeTotal , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("In the past 30 days, what was the total income (from employment) of all the hous",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("In the past 30 days, what was the total income (from employment) of all the hous",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Over the past 30 days, what was the total household expenditure? (In local curre
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Over the past 30 days, what was the total household expenditure? (In local curre",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Over the past 30 days, what was the total household expenditure? (In local curre",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureTotalx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureTotal , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Over the past 30 days, what was the total household expenditure? (In local curre",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Over the past 30 days, what was the total household expenditure? (In local curre",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on food
Do you share this with anyone who is not registered on the same case as you? Ask Paolo how to deal with situation where our sample unit does not live on their own and how do we record expenditure


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on food",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on food",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFoodx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFood , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on food",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on food",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on health and medical cost
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on health and medical cost",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on health and medical cost",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealthx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHealth , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on health and medical cost",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on health and medical cost",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on education costs (includ
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on education costs (includ",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on education costs (includ",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducationx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEducation , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on education costs (includ",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on education costs (includ",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on rent
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on rent",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on rent",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRentx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureRent , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on rent",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on rent",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on shelter materials
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on shelter materials",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on shelter materials",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelterx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureShelter , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on shelter materials",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on shelter materials",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on water
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on water",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on water",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWaterx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureWater , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on water",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on water",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on gas
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on gas",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on gas",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGasx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureGas , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on gas",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on gas",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on fuel (do not include fu
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on fuel (do not include fu",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on fuel (do not include fu",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuelx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureFuel , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on fuel (do not include fu",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on fuel (do not include fu",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on transport (including fu
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on transport (including fu",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on transport (including fu",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransportx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTransport , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on transport (including fu",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on transport (including fu",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on electricity
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on electricity",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on electricity",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricityx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureElectricity , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on electricity",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on electricity",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on clothing
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on clothing",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on clothing",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothingx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureClothing , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on clothing",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on clothing",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on communications (mobile,
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on communications (mobile,",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on communications (mobile,",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureCommx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureComm , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on communications (mobile,",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on communications (mobile,",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on soap and other househol
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on soap and other househol",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on soap and other househol",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygienex1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHygiene , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on soap and other househol",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on soap and other househol",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on household items or asse
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on household items or asse",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on household items or asse",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHouseholdx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureHousehold , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on household items or asse",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on household items or asse",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on entertainment
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on entertainment",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on entertainment",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertainx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureEntertain , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on entertainment",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on entertainment",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on alcohol / tobacco / win
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on alcohol / tobacco / win",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on alcohol / tobacco / win",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobaccox1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureTobacco , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on alcohol / tobacco / win",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on alcohol / tobacco / win",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on debt repayment
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on debt repayment",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on debt repayment",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepaymentx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.DebtRepayment , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on debt repayment",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on debt repayment",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household on legal and registration fees (legal residency, b
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household on legal and registration fees (legal residency, b",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household on legal and registration fees (legal residency, b",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentationx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureDocumentation , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household on legal and registration fees (legal residency, b",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household on legal and registration fees (legal residency, b",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Amount spent by the household during the past 30 days on all other expenditures,
NA


Numeric question  


### Tabulation

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}

MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers <- as.numeric(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers)
frequ <- as.data.frame(table(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers))
average <- as.data.frame(svymean(~ Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers, design = MainDataFrame.survey, na.rm = TRUE))
cat(paste0("Based on the sample design, the average weighted mean response for this question is ", as.numeric(round(average$mean, digits = 2))))
#  regular histogram
plot1 <- ggplot(data = frequ, aes(x = frequ$Var1, y = frequ$Freq)) +
geom_bar(fill = "#2a87c8",colour = "white", stat = "identity", width = .8) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on all other expenditures,",subtitle = "Before data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
data.outlier <- MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers
data.nooutlier <- as.data.frame(MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers)
qnt <- quantile(data.outlier, probs = c(.25, .75), na.rm = T)
caps.df <- as.data.frame(quantile(data.outlier, probs = c(.05, .95), na.rm = T))
H  <- 1.5 * IQR(data.outlier, na.rm = T)
data.nooutlier[(data.nooutlier < (qnt[1] - H)) & !(is.na(data.nooutlier))  ] <- caps.df[1,1]
data.nooutlier[ (data.nooutlier > (qnt[2] + H)) & !(is.na(data.nooutlier)) ] <- caps.df[2,1]
names(data.nooutlier)[1] <- "variable"
plot1 <- ggplot(data = data.nooutlier, aes(x = data.nooutlier$variable)) +
geom_histogram(color = "white",fill = "#2a87c8", breaks = pretty(data.nooutlier$variable, n = nclass.Sturges(data.nooutlier$variable),min.n = 1)) +
labs(x = "", y = "Count") +
ggtitle("Amount spent by the household during the past 30 days on all other expenditures,",
subtitle = "After data capping treatement.") +
kobo_unhcr_style_histo()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```

### Analysis of relationship

```{r Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthersx1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}


plot1 <- ggplot(MainDataFrame, aes(y=MainDataFrame$Welfare.IncomeExpenditure.Expenditure.ExpenditureAll.ExpenditureOthers , x=MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") + 
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on all other expenditures,",
subtitle = "Before data capping treatement, by question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)
## Boxplot
plot1 <- ggplot(MainDataFrame, aes(y=data.nooutlier$variable, x= MainDataFrame$Location.LocationDistrict)) +
geom_boxplot(fill="#2a87c8",colour="black") +  #notch=TRUE
scale_size_area(max_size = 10) +
guides(fill = FALSE) +
xlab("") +
ylab("") +
coord_flip() +
scale_y_continuous(breaks= pretty_breaks()) +
ggtitle("Amount spent by the household during the past 30 days on all other expenditures,",
subtitle = "After data capping treatement. By question: District") +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


 
## Does the household currently receive multi-purpose cash assistance?
NA


Single choice question 


### Tabulation
```{r Assistance.AssistanceDetails.CashAssistance.tab, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=1.66666666666667, size="small"}
### Tabulation
##Compute contengency table
frequ <- as.data.frame(table(MainDataFrame$Assistance.AssistanceDetails.CashAssistance))
frequ[ ,1] = factor(frequ[ ,1],levels(frequ[ ,1])[order(frequ$Freq, decreasing = FALSE)])
frequ <- frequ[ order(frequ[ , 1]) ,  ]
names(frequ)[1] <- "CashAssistance"
## Frequency table with NA in order to get non response rate
frequ1 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.AssistanceDetails.CashAssistance, useNA = "ifany")))
frequ1 <- frequ1[!(is.na(frequ1$Var1)), ]
frequ1 <- frequ1[!(frequ1$Var1 == "NA"), ]
percentreponse <- paste0(round(sum(frequ1$Freq)*100,digits = 1),"%")
## Frequency table without NA
frequ2 <- as.data.frame(prop.table(table(MainDataFrame$Assistance.AssistanceDetails.CashAssistance,useNA = "no")))
## Frequency table with weight
frequ.weight <- as.data.frame(svymean(~ Assistance.AssistanceDetails.CashAssistance, design = MainDataFrame.survey, na.rm = TRUE))
## Binding the two
frequ3 <- cbind(frequ2,frequ.weight)
## Reorder factor
frequ3[ ,1] = factor(frequ3[ ,1],levels(frequ3[ ,1])[order(frequ3$mean, decreasing = FALSE)])
frequ3 <- frequ3[ order(frequ3[ , 1]) ,  ]
frequ3[ ,5] <- paste0(round(frequ3[ ,3]*100,digits = 1),"%")
names(frequ3)[5] <- "freqper2"


## and now the graph
plot1 <- ggplot(frequ3, aes(x = frequ3$Var1, y = frequ3$mean)) +
geom_bar(fill = "#2a87c8", colour = "#2a87c8", stat = "identity", width=.8) +
guides(fill = FALSE) +
geom_label_repel(aes(y = mean, label = freqper2), fill = "#2a87c8", color = 'white') +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
xlab("") +
coord_flip() +
ggtitle("Does the household currently receive multi-purpose cash assistance?",
subtitle = paste0(" Question response rate: ",percentreponse," .")) +
kobo_unhcr_style_bar()
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```






### Cross-tabulations


```{r Assistance.AssistanceDetails.CashAssistance1.rel, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "", fig.height=4, size="small"}
crosssfrequ.weight <-as.data.frame(prop.table(svytable(~Assistance.AssistanceDetails.CashAssistance + Location.LocationDistrict, design =MainDataFrame.survey  ), margin = 2))
names(crosssfrequ.weight)[1] <- "quest"
names(crosssfrequ.weight)[2] <- "disag"
crosssfrequ.weight$Freq2 <- paste0(round(crosssfrequ.weight$Freq*100,digits = 1),"%")
## Reorder factor
cross <- dcast(crosssfrequ.weight, disag  ~ quest, value.var = "Freq")
cross <- cross[ order(cross[ ,2], decreasing = FALSE) ,  ]
crosssfrequ.weight$disag <- factor(crosssfrequ.weight$disag, levels = as.character(cross[ ,1]))


## and now the graph
plot1 <- ggplot(crosssfrequ.weight, aes(fill=crosssfrequ.weight$quest, y=crosssfrequ.weight$Freq, x = crosssfrequ.weight$disag)) +
geom_bar(colour="white", stat ="identity", width=.8, aes(fill = quest), position = position_stack(reverse = TRUE)) +
ylab("Frequency") +
scale_y_continuous(labels = percent) +
scale_fill_viridis(discrete=TRUE) +
xlab("") +
coord_flip() +
ggtitle("Does the household currently receive multi-purpose cash assistance? (color)",
subtitle = " By question: District (bar)") +
kobo_unhcr_style_bar() +
theme(legend.direction = "horizontal", legend.position = "bottom", legend.box = "horizontal",legend.title=element_blank()  )
ggpubr::ggarrange(kobo_left_align(plot1, c("subtitle", "title")), ncol = 1, nrow = 1)

```


### Significant Associations (chi-square with p value < 5%)

No significant association found for this question...

##### Page Break
